Exploring United States Housing Affordability

### 2016-08-09 paper/Paper.Rmd
editing graphs and text

  clean_years %>%
    mutate(per = cut(per, 
                     breaks = c(0, 1, 2, Inf),
                     labels = c("1", "2", "3 or more")))  %>%
    group_by(year, per) %>%  
    # Take the median instead of mean to avoid extreme observations skewing the 
    # result.
    summarise(new_y = median(burden, na.rm = T)) %>%
    ggplot(aes(x = year,   
                      y = new_y,   
                      colour = per)) +  
    geom_line(size = 1) +
    labs(colour = "Household size",
         x = "Year",
         y = "Median burden") +
    scale_colour_brewer(palette = "Dark2") +
  scale_y_continuous(labels=function(x){paste0(x*100, "%")}) +
  theme_minimal(base_family = "serif")

@@

  This graph shows the development of median burden (proportion of housing costs relative to household income) from 1985 to 2013. The median burden varies dramatically between households of different sizes. The highest burden through the years has been on households of one person. This is understandable, since people living alone cannot split any costs between other earners.
  Surprisingly, households of two people have the lowest burdens overall. Our hypothesis is that this is due to a large proportion of two-earner couples in this group. As housing cost burden is simply a household's monthly housing cost divided by its monthly income, households where all members are earners have a higher monthly income and a lower resulting burden. In households of 3 or more people, the burden picks up again. This is likely due to a larger amount of children and / or retirees in larger households. Also, households with 3 or more members tend to hae only one earner.
  Another interesting thing is the dramatic increase of burden during the buildup to the financial crisis 2000-2007. The most probable exlanation is the housing market price bubble. Once the crisis hit in 2007, the effect of dropping incomes continued to increase burdens until 2011. Only in 2013 data did the burdens start to fall from the unprecedently high levels.

```{r, include = F, fig.cap="Median Income across Census Regions"}
url <- "http://www.mapsofworld.com/usa/usa-maps/united-states-regional-maps.html"
html <- read_html(url)
xpath <- '//table[@class="tableizer-table"]'

@@

median_incomes <- clean_years %>%
  mutate(region = as.character(region)) %>%
  group_by(region) %>%
  summarise(zinc2_median = median(zinc2, na.rm = T))

map_df <- map_data("state") %>%
  mutate(region = str_to_title(region)) %>%
  rename(state = region)  %>%
  # Join with census region information
  left_join(regions) %>%
  left_join(median_incomes)

usa_map <- map_df %>% 
  ggplot() +  
  geom_polygon(aes(x=long, 
                   y = lat, 
                   fill = zinc2_median, 
                   group = group)) + 
  coord_fixed(1.3) +
  theme_minimal(base_family = "serif") +
  scale_x_continuous(name = NULL,
                     labels = NULL,
                     breaks = NULL) +
  scale_y_continuous(name = NULL,
                     labels = NULL,
                     breaks = NULL) +
  labs(fill = "Median income") +
  scale_fill_distiller(limits = c(25000, 42000), 
                                 breaks = sort(unique(map_df$zinc2_median),
                                               decreasing = T),
                                 palette = "Greens", 
                                 direction = 1,
                                 guide = "legend",
                        labels=function(x){paste0("$",x %/% 100 / 10, "K")})
```

```{r, echo=F, fig.cap="Median Income across Census Regions"}
usa_map
```

  To gauge income levels in different areas we used the four census regions in the dataset and joined them with a scraped table from mapsoftheworld.com. Using the table we could connect census regions to state names and thus colour a map of the continental US with census region incomes. We used median incomes instead of mean incomes to avoid skewing the results with outliers.
  The household median monthly incomes vary between different census regions from 32200 dollars in the South to nearly 25% higher, 40000, in the West. The Northeast trails closely behind the West with 37267.50 dollars, and the Midwest is closer to the South with a median income of 35000.
  While the dataset doesn't have more granular location data, even these four regions are very distinct from each other. The large high-income cities in the Northeast and the West likely contribute to the higher respective median incomes, while more rural Midwest and South are poorer.

```{r, echo = FALSE}
regionNames = c("1" = "Northeast", "2" = "Midwest", "3" = "South", "4" = "West")

@@

```{r, echo = FALSE, fig.height=1, fig.cap='Median Adjusted Income per person (left) and per bedroom (right)'}
ggplot() + theme(panel.background = element_rect(fill = 'white', colour = 'white'))
```

@@

  In order to better understand the regional differences in income, the incomes were adjusted by certain variables. 
  The first plot compares APLmed by year for the four regions in the United States (Northeast, South, Midwest, West). APLmed is the adjusted median household income per person. This was precaculated using Housing and Urban Development (HUD) indexes. For example, a one person household's income is adjusted by a factor of 0.70, two by 0.80, and so on with a four person household being adjusted by 1.00 (or having no change from the median household income). The reason for no adjustment to a four person household income is because the median household size in the United States is about four persons. 
  It is clear that the Northeast and the West are the most expensive regions. This is makes sense given that the northeast and West are by far the most productive (by GDP) regions in the United States. 
  The median adjusted income increases steadily (roughly linearly) over time. There is a decrease in income around 2010, correlated to the economic recession with a 2 year lag between the Northeast and the rest of the regions.The reason for this lag may be due to the fact that the financial center of the United States lies in the northeast, around New York City. So, when the 2008 crisis occurred the repercussions were immediately felt in the Northeast (Wall Street and Main Street- which refers to the Washington D.C. economy) while the other regions took some time to correct for the downturn in the financial market.
  The second plot of the graph depicts ABLmed versus year. ABLmed signifies the median adjusted income for the number of bedrooms in a household's living quarters. ABlmed was calculated using precaculated HUD indexes. Here, zero bedrooms was adjusted by a factor of 0.70, two bedrooms by 0.90, and so on. Three bedroom properties were adjusted by a factor of 1.04, because the median number of bedrooms in a property is roughly three bedrooms
  It is interesting to note that the disparity between the incomes increases between the Northeast and Western regions and the Midwest and South. This is likely because those living in the Midwest and South tend to live in larger homes, housing more bedrooms on average, relative to their incomes due to the higher housing affordability. However, this should mean that their incomes go 'further,' as they have more purchasing parity given the lower cost of living compared to the Northeast and the West. This is not shown in the graphs, which indicate that the income levels are significantly different. However, if housing affordability was factored into the calculation, the income disparity would be far less if not almost nonexistent. The lag in the downward trend after 2008 still occurs in the plots.
  With the income information in hand, the burden data can be explored in further detail.

```{r, echo = FALSE, fig.cap="Amount of households relative to poverty line"}
clean_years %>% 
  # Group and summarise the amount of people in each poverty group each year
  group_by(fmtincrelpovcat, year) %>%
  summarise(count = n()) %>%
  # Clean NAs
  na.omit() %>%
  # Group again by year to calculate relative percentages per year
  group_by(year) %>% 
  mutate(percent = count / sum(count),  
         # Clean the labels
         fmtincrelpovcat = factor(fmtincrelpovcat, 
                                  levels = c("1 LTE Poverty", 
                                             "2 100-150% Poverty", 
                                             "3 150-200% Poverty", 
                                             "4 200%+ Poverty"),  
                                  labels = c("Less than poverty income",   
                                             "100-150% of poverty income",   
                                             "150-200% of poverty income",    
                                             "> 200% of poverty income"),
                                  ordered = T)) %>% 
  ggplot(aes(x = year, 
             y = percent,
             fill = fmtincrelpovcat)) + 
  geom_area(alpha = 0.8) +
  # Use a nice colour palette
  scale_fill_brewer(palette = "RdYlGn", 
                    # Reverse the order of legend items to match the
                    # stacking order
                    guide = guide_legend(reverse=TRUE)) +
  labs(x = "Year",
       y = "Percent of households",
       fill = "Household income
relative to poverty income") +
  scale_y_continuous(labels=function(x){paste0(x*100, "%")}) +
  scale_colour_brewer(palette = "Dark2") +
  theme_minimal(base_family = "serif") 
```

  This plot shows the amount of households in a given income group in a given year. Each household has been calculated a poverty treshold according to the Census Bureau’s official thresholds, based on family size and number of children. 
  As can be seen from the plot, the amount of people in different income groups stayed relatively constant between 1985 and 2007. The majority of people earned over twice the poverty income, while little under a fifth of the population was in poverty. This stable relationship broke noticeably in the financial crisis of 2007 and the following recession, when the amount of people in poverty started a quite steep and steady climb upwards. 
  Interestingly, the income brackets of 100%-200% stayed almost exactly the same size as before, while the increase in poverty was in effect solely the result of the dwindling of the highest (over 200% of poverty income) income bracket. A reasonable explanation would be the effect of increasing unemployment, with previously employed well-off people dropping to unemployment and thus small or no income. The reality can be more nuanced, with people dropping to the middle income groups and a simultaneous equally large movement from these brackets to poverty, but the big picture of large impacts in poverty following the financial crisis stays the same.

```{r, echo = FALSE, fig.cap="Relationship between Household Income and Burden"}
###### Household Income
  ####overall graph
clean_years %>% 
  select(zinc2, year, region, fmtburden)%>% 
  filter(fmtburden != ".", fmtburden != "4 No Income") %>% 
  mutate(fmtburden = str_replace(fmtburden, "Greater than 50%", "50% or More")) %>% 
  group_by_("year", "fmtburden") %>%  
  summarise_(new_y = as.formula(
  paste0("~ median(","zinc2", ",na.rm=T)"))) %>% 
  ggplot(aes_string(x = "year", y = "new_y", color = "fmtburden")) + 
  geom_line(size = 1) + 
  labs(y = "Household Income", x = "Year", color = "Burden") +
  scale_y_continuous(limits=c(0,NA),breaks=c(0,20000,40000,60000),labels=function(x){paste0(x/1000, "K")}) +
  scale_colour_brewer(palette = "Dark2") +
  theme_minimal(base_family = "serif")

@@

```{r, echo = FALSE, fig.cap="Relationship between Household Income and Burden"}
 ### faceted by region 
clean_years %>%  
  mutate(fmtburden = str_replace(fmtburden, "Greater than 50%", "50% or More")) %>%
  filter(fmtburden != "4 No Income") %>% 
  group_by_("year","region", "fmtburden") %>%  
  summarise_(new_y = as.formula(
    paste0("~ median(","zinc2", ",na.rm=T)"))) %>% 
  ggplot(aes_string(x = "year", y = "new_y", color = "fmtburden")) + 
  geom_line(size = 1) + 
  facet_wrap(~region, labeller = as_labeller(regionNames)) +
  labs(y = "Household Income ($)", x = "Year", color = "Burden") +
  scale_y_continuous(limits=c(0,NA),breaks=c(0,25000,50000,75000),labels=function(x){paste0(x/1000, "K")}) +
  scale_colour_brewer(palette = "Dark2") +
  theme_minimal(base_family = "serif")

  From this graph, you can see that the Northeast and West have higher rates of burden at higher income levels, therefore illustrating how housing affordability in these regions are less than that of the Midwest and South.

@@

####overall graph
cleanyearsmonthly %>%  
  group_by_("year", "fmtburden") %>%  
  summarise_(new_y = as.formula(
    paste0("~ median(","zsmhc", ",na.rm=T)"))) %>%

  ggplot(aes_string(x = "year", y = "new_y", color = "fmtburden")) + 
  geom_line(size = 1) + 
  labs(y = "Monthly Housing Costs ($)", x = "Year", color = "Burden") +
  scale_colour_brewer(palette = "Dark2") +
  theme_minimal(base_family = "serif")

@@

### faceted by region
  cleanyearsmonthly %>%  
  group_by_("year","region", "fmtburden") %>%  
  summarise_(new_y = as.formula(
    paste0("~ median(","zsmhc", ",na.rm=T)"))) %>% 
  ggplot(aes_string(x = "year", y = "new_y", color = "fmtburden")) + 
  geom_line(size = 1) + 
  facet_wrap(~region, labeller = as_labeller(regionNames)) + 
  labs(y = "Monthly Housing Costs ($)", x = "Year", color = "Burden") +
  scale_colour_brewer(palette = "Dark2") +
  theme_minimal(base_family = "serif")

@@

  From this graph, you can see that the Northeast and West have higher rates of burden at higher income levels, therefore illustrating how housing affordability in these regions are less than that of the Midwest and South.

```{r, fig.width=12, fig.height=6,echo = F, message=F,error=F, warning=FALSE, fig.cap = "Income compared to area's median grouped by house type"}
clean_years %>% 
  filter(fmtstructuretype != ".") %>% 
      # Use NSE
      group_by_("year", "fmtstructuretype") %>%  
      # Take the median instead of mean to avoid extreme observations skewing the 
      # result.
      summarise_(new_y= as.formula(paste0("~ median(","increlamipct", ",na.rm=T)"))) %>%  
      # Use NSE
      ggplot(aes_string(x = "year",   
                        y = "new_y",   
                        colour = "fmtstructuretype")) +  
  geom_line(size = 1) +
  scale_y_continuous(labels=function(x){paste0(x*100, "%")}) +
  labs(colour = "Structure Type",
       y="Income percentage of area median income",
       x = "Year") +
  scale_colour_brewer(palette = "Dark2") +
  theme_minimal(base_family = "serif")

>>>>

  clean_years %>%
    mutate(per = cut(per, 
                     breaks = c(0, 1, 2, Inf),
                     labels = c("1", "2", "3 or more")))  %>%
    group_by(year, per) %>%  
    # Take the median instead of mean to avoid extreme observations skewing the 
    # result.
    summarise(new_y = median(burden, na.rm = T)) %>%
    ggplot(aes(x = year,   
                      y = new_y,   
                      colour = per)) +  
    geom_line(size = 1) +
    labs(colour = "Household Size",
         x = "Year",
         y = "Median Burden") +
    scale_colour_brewer(palette = "Dark2") +
  scale_y_continuous(labels=function(x){paste0(x*100, "%")}) +
  theme_minimal(base_family = "serif")

@@

  This graph shows the development of median burden (proportion of housing costs relative to household income) from 1985 to 2013. The median burden varies dramatically between households of different sizes. The highest burden through the years has been on households of one person. This is understandable, since people living alone cannot split any costs between other earners.

  Surprisingly, households of two people have the lowest burdens overall. Our hypothesis is that this is due to a large proportion of two-earner couples in this group. As housing cost burden is simply a household's monthly housing cost divided by its monthly income, households where all members are earners have a higher monthly income and a lower resulting burden. In households of 3 or more people, the burden picks up again. This is likely due to a larger amount of children and / or retirees in larger households. Also, households with 3 or more members tend to hae only one earner.

  Another interesting thing is the dramatic increase of burden during the buildup to the financial crisis 2000-2007. The most probable exlanation is the housing market price bubble. Once the crisis hit in 2007, the effect of dropping incomes continued to increase burdens until 2011. Only in 2013 data did the burdens start to fall from the unprecedently high levels.

```{r, include = F, fig.cap = "Median Income Across Census Regions"}
url <- "http://www.mapsofworld.com/usa/usa-maps/united-states-regional-maps.html"
html <- read_html(url)
xpath <- '//table[@class="tableizer-table"]'

@@

median_incomes <- clean_years %>%
  filter(year == 2013) %>%
  mutate(region = as.character(region)) %>%
  group_by(region) %>%
  summarise(zinc2_median = median(zinc2, na.rm = T))

us_map <- map_data("state") %>%
  mutate(region = str_to_title(region)) %>%
  rename(state = region)  %>%
  # Join with census region information
  left_join(regions) %>%
  left_join(median_incomes)

us_map %>% 
  ggplot() +  
  geom_polygon(aes(x=long, 
                   y = lat, 
                   fill = zinc2_median, 
                   group = group)) + 
  coord_fixed(1.3) +
  theme_tufte(base_size = 20, base_family = "serif") +
  scale_x_continuous(name = NULL,
                     labels = NULL,
                     breaks = NULL) +
  scale_y_continuous(name = NULL,
                     labels = NULL,
                     breaks = NULL) +
  labs(fill = "Median income") +
  scale_fill_distiller(limits = c(35000, 54000), 
                                 breaks = sort(unique(us_map$zinc2_median),
                                               decreasing = T),
                                 palette = "Greens", 
                                 direction = 1,
                                 guide = "legend",
                        labels=function(x){paste0("$",
                                                  x %/% 100 / 10, "K")})
```

  To gauge income levels in different areas we used the four census regions in the dataset and joined them with a scraped table from mapsoftheworld.com. Using the table we could connect census regions to state names and thus colour a map of the continental US with census region incomes. We used median incomes instead of mean incomes to avoid skewing the results with outliers.

  The household median monthly incomes vary between different census regions from 32200 dollars in the South to nearly 25% higher, 40000, in the West. The Northeast trails closely behind the West with 37267.50 dollars, and the Midwest is closer to the South with a median income of 35000.

  While the dataset doesn't have more granular location data, even these four regions are very distinct from each other. The large high-income cities in the Northeast and the West likely contribute to the higher respective median incomes, while more rural Midwest and South are poorer.

```{r, echo = FALSE}

regionNames = c("1" = "Northeast", "2" = "Midwest", "3" = "South", "4" = "West")

@@

```{r, echo = FALSE, fig.height=1, fig.cap='Median Adjusted Income per person (left) and per bedroom (right)'}

ggplot() + theme(panel.background = element_rect(fill = 'white', colour = 'white'))
```

@@

  In order to better understand the regional differences in income, the incomes were adjusted by certain variables.

  The first plot compares APLmed by year for the four regions in the United States (Northeast, South, Midwest, West). APLmed is the adjusted median household income per person. This was precaculated using Housing and Urban Development (HUD) indexes. For example, a one person household's income is adjusted by a factor of 0.70, two by 0.80, and so on with a four person household being adjusted by 1.00 (or having no change from the median household income). The reason for no adjustment to a four person household income is because the median household size in the United States is about four persons.

  It is clear that the Northeast and the West are the most expensive regions. This is makes sense given that the northeast and West are by far the most productive (by GDP) regions in the United States.

  The median adjusted income increases steadily (roughly linearly) over time. There is a decrease in income around 2010, correlated to the economic recession with a 2 year lag between the Northeast and the rest of the regions.The reason for this lag may be due to the fact that the financial center of the United States lies in the northeast, around New York City. So, when the 2008 crisis occurred the repercussions were immediately felt in the Northeast (Wall Street and Main Street- which refers to the Washington D.C. economy) while the other regions took some time to correct for the downturn in the financial market.

  The second plot of the graph depicts ABLmed versus year. ABLmed signifies the median adjusted income for the number of bedrooms in a household's living quarters. ABlmed was calculated using precaculated HUD indexes. Here, zero bedrooms was adjusted by a factor of 0.70, two bedrooms by 0.90, and so on. Three bedroom properties were adjusted by a factor of 1.04, because the median number of bedrooms in a property is roughly three bedrooms

  It is interesting to note that the disparity between the incomes increases between the Northeast and Western regions and the Midwest and South. This is likely because those living in the Midwest and South tend to live in larger homes, housing more bedrooms on average, relative to their incomes due to the higher housing affordability. However, this should mean that their incomes go 'further,' as they have more purchasing parity given the lower cost of living compared to the Northeast and the West. This is not shown in the graphs, which indicate that the income levels are significantly different. However, if housing affordability was factored into the calculation, the income disparity would be far less if not almost nonexistent. The lag in the downward trend after 2008 still occurs in the plots.
  With the income information in hand, the burden data can be explored in further detail.

```{r, echo = FALSE, fig.cap = "Amount of households relative to poverty line"}
clean_years %>% 
  # Group and summarise the amount of people in each poverty group each year
  group_by(fmtincrelpovcat, year) %>%
  summarise(count = n()) %>%
  # Clean NAs
  na.omit() %>%
  # Group again by year to calculate relative percentages per year
  group_by(year) %>% 
  mutate(percent = count / sum(count),  
         # Clean the labels
         fmtincrelpovcat = factor(fmtincrelpovcat, 
                                  levels = c("1 LTE Poverty", 
                                             "2 100-150% Poverty", 
                                             "3 150-200% Poverty", 
                                             "4 200%+ Poverty"),  
                                  labels = c("Less than poverty income",   
                                             "100-150% of poverty income",   
                                             "150-200% of poverty income",    
                                             "> 200% of poverty income"),
                                  ordered = T)) %>% 
  ggplot(aes(x = year, 
             y = percent,
             fill = fmtincrelpovcat)) + 
  geom_area(alpha = 0.8) +
  # Use a nice colour palette
  scale_fill_brewer(palette = "RdYlGn", 
                    # Reverse the order of legend items to match the
                    # stacking order
                    guide = guide_legend(reverse=TRUE)) +
  labs(x = "Year",
       y = "Percent of Households",
       fill = "Household Income
Relative to Poverty Income") +
  scale_y_continuous(labels=function(x){paste0(x*100, "%")}) +
  scale_colour_brewer(palette = "Dark2") +
  theme_minimal(base_family = "serif") 
```

  This plot shows the amount of households in a given income group in a given year. Each household has been calculated a poverty treshold according to the Census Bureau’s official thresholds, based on family size and number of children.

  As can be seen from the plot, the amount of people in different income groups stayed relatively constant between 1985 and 2007. The majority of people earned over twice the poverty income, while little under a fifth of the population was in poverty. This stable relationship broke noticeably in the financial crisis of 2007 and the following recession, when the amount of people in poverty started a quite steep and steady climb upwards.

  Interestingly, the income brackets of 100%-200% stayed almost exactly the same size as before, while the increase in poverty was in effect solely the result of the dwindling of the highest (over 200% of poverty income) income bracket. A reasonable explanation would be the effect of increasing unemployment, with previously employed well-off people dropping to unemployment and thus small or no income. The reality can be more nuanced, with people dropping to the middle income groups and a simultaneous equally large movement from these brackets to poverty, but the big picture of large impacts in poverty following the financial crisis stays the same.

```{r, echo = FALSE, fig.cap="Relationship between Household Income and Burden"}
###### Household Income
  ####overall graph
clean_years %>% 
  select(zinc2, 
         year, 
         region, 
         fmtburden)%>% 
  filter(fmtburden != ".", 
         fmtburden != "No Income") %>% 
  mutate(fmtburden = str_replace(fmtburden, 
                                 "Greater than 50%", 
                                 "50% or More")) %>% 
  group_by_("year", "fmtburden") %>%  
  summarise_(new_y = as.formula(
  paste0("~ median(","zinc2", ",na.rm=T)"))) %>% 
  ggplot(aes_string(x = "year", 
                    y = "new_y", 
                    color = "fmtburden")) + 
  geom_line(size = 1) + 
  labs(y = "Household Income", 
       x = "Year", 
       color = "Burden") +
  scale_y_continuous(limits = c(0,NA), 
                     breaks=c(0,20000,40000,60000),
                     labels=function(x){paste0("$",x/1000, "K")}) +
  scale_colour_brewer(palette = "Dark2") +
  theme_minimal(base_family = "serif")

@@

@@

cleanyearsmonthly %>%  
  group_by_("year", "fmtburden") %>%  
  summarise_(new_y = as.formula(
    paste0("~ median(","zsmhc", ", na.rm=T)"))) %>%

  ggplot(aes_string(x = "year", 
                    y = "new_y", 
                    color = "fmtburden")) + 
  geom_line(size = 1) + 
  labs(y = "Monthly Housing Costs", 
       x = "Year", 
       color = "Burden") +
  scale_y_continuous(labels=function(x){paste0("$", x)}) +
  scale_colour_brewer(palette = "Dark2") +
  theme_minimal(base_family = "serif")

@@

### faceted by region
  cleanyearsmonthly %>%  
  group_by_("year","region", "fmtburden") %>%  
  summarise_(new_y = as.formula(
    paste0("~ median(","zsmhc", ",na.rm=T)"))) %>% 
  ggplot(aes_string(x = "year", y = "new_y", color = "fmtburden")) + 
  geom_line(size = 1) + 
  facet_wrap(~region, labeller = as_labeller(regionNames)) + 
  labs(y = "Monthly Housing Costs", x = "Year", color = "Burden") +
  scale_y_continuous(labels=function(x){paste0("$", x)}) +
  scale_colour_brewer(palette = "Dark2") +
  theme_minimal(base_family = "serif")

@@

  From this graph, you can see that the Northeast and West have higher rates of burden at higher income levels, therefore illustrating how housing affordability in these regions are less than that of the Midwest and South. From this graph, you can see that the Northeast and West have higher rates of burden at higher income levels, therefore illustrating how housing affordability in these regions are less than that of the Midwest and South.

```{r, fig.width=12, fig.height=6,echo = F, message=F,error=F, warning=FALSE, fig.cap = "Income compared to area's median grouped by house type"}
clean_years %>% 
  filter(fmtstructuretype != ".") %>% 
      # Use NSE
      group_by_("year", "fmtstructuretype") %>%  
      # Take the median instead of mean to avoid extreme observations skewing the 
      # result.
      summarise_(new_y= as.formula(paste0("~ median(","increlamipct", ",na.rm=T)"))) %>%  
      # Use NSE
      ggplot(aes_string(x = "year",   
                        y = "new_y",   
                        colour = "fmtstructuretype")) +  
  geom_line(size = 1) +
  scale_y_continuous(labels = function(x){paste0(x, "%")}) +
  labs(colour = "Structure Type",
       y = "Income Percentage of Area Median Income",
       x = "Year") +
  scale_colour_brewer(palette = "Dark2") +
  theme_minimal(base_family = "serif")
